---
title: "LinearModels"
author: "Chirag Shah"
date: '2018-11-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

Cleaning data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group,
         neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Price as outcome variable

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(boro = fct_infreq(boro),
         room_type = fct_infreq(room_type))

fit = lm(price ~ stars + boro, data = nyc_airbnb)
```

Tidying output 

```{r}
summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
```

The broom package has functions for obtaining a quick summary of the model and for cleaning up the coefficient table.

```{r}
fit %>% 
  broom::glance()

fit %>% 
  broom::tidy()
```

Both of these functions produce data frames, which makes it straightforward to include the results in subsequent steps.
```{r}
fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```
Now you are changing the reference variable by room_type frequency. the lowest frequency is the reference

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(boro = fct_infreq(boro),
         room_type = fct_infreq(room_type))

fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()
```

Now manhattan is the ref

Diagnostics

```{r}
modelr::add_residuals(nyc_airbnb, fit)

modelr::add_predictions(nyc_airbnb, fit)
```

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = boro, y = resid)) + geom_violin()
```

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()

##other methods
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()

nyc_airbnb %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = stars, y = pred, color = boro)) + geom_point()
```

## Testing
For testing a single coefficient you are already getting the hypothesis test using broom::tidy


```{r}
fit_null = lm(price ~ stars + boro, data = nyc_airbnb)
fit_alt = lm(price ~ stars + boro + room_type, data = nyc_airbnb)
```

```{r}
anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

Nesting data

Interaction term
```{r}
nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Alternatively, we can nest within boroughs and fit borough-specific models associating price with rating and room type:
Nesting and then fitting
```{r}
nest_lm_res =
  nyc_airbnb %>% 
  group_by(boro) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest()
```

The results of this approach are given in the table below.

```{r}
nest_lm_res %>% 
  select(boro, term, estimate) %>% 
  mutate(term = fct_inorder(term)) %>% 
  spread(key = term, value = estimate) %>% 
  knitr::kable(digits = 3)
```

An even more extreme example is the assessment of neighborhood effects in Manhattan. The code chunk below fits neighborhood-specific models:

```{r}
manhattan_airbnb =
  nyc_airbnb %>% 
  filter(boro == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb %>% 
  group_by(neighborhood) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest()
```

And the chunk below shows neighborhood-specific estimates for the coefficients related to room type.

```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

```{r}
manhattan_airbnb %>% 
  lme4::lmer(price ~ stars + room_type + (1 + room_type | neighborhood), data = .) %>% 
  broom::tidy()
```
Binary Models
```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") %>% 
  filter(city == "Baltimore") %>% 
  mutate(resolved = as.numeric(disposition == "Closed by arrest"),
         victim_age = as.numeric(victim_age),
         victim_race = fct_relevel(victim_race, "White")) %>% 
  select(resolved, victim_age, victim_race, victim_sex)
```

Using these data, we can fit a logistic regression for the binary “resolved” outcome and victim demographics as predictors. This uses the glm function with the family specified to account for the non-Gaussian outcome distribution.

```{r}
fit_logistic = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 
```

Many of the same tools we used to work with lm fits can be used for glm fits. The table below summaries the coefficients from the model fit; because logistic model estimates are log odds ratios, we include a step to compute odds ratios as well.

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```

We can also compute fitted values; similarly to the estimates in the model summary, these are expressed as log odds and can be transformed to produce probabilities for each subject.

```{r}
baltimore_df %>% 
  modelr::add_predictions(fit_logistic) %>% 
  mutate(fitted_prob = boot::inv.logit(pred))
```

